---
title: "Amazon_stock_analysis"
author: "Daniel Jung"
date: "4/20/2020"
output: html_document
---

## Front Matter

```{r}
# clean up workspace environment
rm(list = ls())
# all packages used for the assignment
library(mosaicData)
library(DataComputing)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(lubridate)
```

# Amazon stock price data (1997 ~ 2020)
```{r}
amzn <- read.csv("AMZN.csv")
```

# Make date data as date data type
```{r}
amzn$Date <- as.Date(amzn$Date)
```

# Line graph on stock price data
```{r}
ggplot(amzn, aes(x = Date, y = Close)) + geom_line()
```

# Mutate about whether close price increased or decreased compared to yesterday
```{r}
amzn <- amzn %>%
          mutate(Change = (Close - lag(Close))/lag(Close)*100)

amzn$Change[1] <- 0
```

# Get three more columns "Year", "Month", "Day"
```{r}
amzn <- amzn %>%
          mutate(year = as.numeric(format(amzn$Date, format = "%Y"))) %>% mutate(month = as.numeric(format(amzn$Date, format = "%m"))) %>% mutate(day = as.numeric(format(amzn$Date, format = "%d")))
```

# Get year high and year low closing price
```{r}
year_high_low <- amzn %>%
                    group_by(year) %>%
                    summarise(year_high = max(Close), year_low = min(Close))
```

# Join two data frame
```{r}
amzn <- amzn %>%
          left_join(year_high_low)
```

# Get the rows that were year high and year low
```{r}
year_high_low_history <- amzn %>%
                            filter(Close == year_high | Close == year_low)
```

# Row number of rows that have year high or year low
```{r}
which(amzn$Close == amzn$year_high)
```

# Get rows from 5 days before to 5 days after for each year-high rows
```{r}
high1 <- amzn$Change[112:122]
high2 <- amzn$Change[409-5:409+5]
high3 <- amzn$Change[650-5:650+5]
high4 <- amzn$Change[665-5:665+5]
high5 <- amzn$Change[932-5:932+5]
high6 <- amzn$Change[1392-5:1392+5]
high7 <- amzn$Change[1614-5:1614+5]
high8 <- amzn$Change[1616-5:1616+5]
high9 <- amzn$Change[1682-5:1682+5]
high10 <- amzn$Change[2160-5:2160+5]
high11 <- amzn$Change[2176-5:2176+5]
high12 <- amzn$Change[2627-5:2627+5]
high13 <- amzn$Change[2675-5:2675+5]
high14 <- amzn$Change[3159-5:3159+5]
high15 <- amzn$Change[3425-5:3425+5]
high16 <- amzn$Change[3630-5:3630+5]
high17 <- amzn$Change[3864-5:3864+5]
high18 <- amzn$Change[4182-5:4182+5]
high19 <- amzn$Change[4198-5:4198+5]
high20 <- amzn$Change[4687-5:4687+5]
high21 <- amzn$Change[4881-5:4881+5]
high22 <- amzn$Change[5169-5:5169+5]
high23 <- amzn$Change[5362-5:5362+5]
high24 <- amzn$Change[5577-5:5577+5]
high25 <- amzn$Change[5768-5:5768+5]
```

# Ten days before and after year-high
```{r}
five_before_after <- data.frame()
five_before_after <- rbind(five_before_after, high1, high2, high3, high4, high5, high6, high7, high8, high9, high10, high11, high12, high13, high14, high15, high16, high17, high18, high19, high20, high21, high22, high23, high24, high25)

colnames(five_before_after) <- c("five_before", "four_before", "three_before", "two_before", "one_before", "the_day", "one_after", "two_after", "three_after", "four_after", "five_after")

five_before_after <- five_before_after[,1:11]
```

# Five days before
```{r}
ggplot(five_before_after, aes(x = five_before)) + geom_density(color = "steelblue", fill = "steelblue") + xlim(-20, 20) + theme_light()
```

# Four days before
```{r}
ggplot(five_before_after, aes(x = four_before)) + geom_density(color = "steelblue", fill = "steelblue") + xlim(-20, 20) + theme_light()
```

# Three days before
```{r}
ggplot(five_before_after, aes(x = three_before)) + geom_density(color = "steelblue", fill = "steelblue") + xlim(-20, 20) + theme_light()
```

# Two days before
```{r}
ggplot(five_before_after, aes(x = two_before)) + geom_density(color = "steelblue", fill = "steelblue") + xlim(-20, 20) + theme_light()
```

# one days before
```{r}
ggplot(five_before_after, aes(x = one_before)) + geom_density(color = "steelblue", fill = "steelblue") + xlim(-20, 20) + theme_light()
```

# The day
```{r}
ggplot(five_before_after, aes(x = the_day)) + geom_density(color = "steelblue", fill = "steelblue") + xlim(-20, 20) + theme_light()
```

# One day after
```{r}
ggplot(five_before_after, aes(x = one_after)) + geom_density(color = "steelblue", fill = "steelblue") + xlim(-20, 20) + theme_light()
```

# Two days after
```{r}
ggplot(five_before_after, aes(x = two_after)) + geom_density(color = "steelblue", fill = "steelblue") + xlim(-20, 20) + theme_light()
```

# Three days after
```{r}
ggplot(five_before_after, aes(x = three_after)) + geom_density(color = "steelblue", fill = "steelblue") + xlim(-20, 20) + theme_light()
```

# Four days after
```{r}
ggplot(five_before_after, aes(x = four_after)) + geom_density(color = "steelblue", fill = "steelblue") + xlim(-20, 20) + theme_light()
```

# Five days after
```{r}
ggplot(five_before_after, aes(x = five_after)) + geom_density(color = "steelblue", fill = "steelblue") + xlim(-20, 20) + theme_light()
```

# Gather data frame to make box plot
```{r}
five_box_plot <- five_before_after %>%
                    pivot_longer(cols = c("five_before", "four_before", "three_before", "two_before", "one_before", "the_day", "one_after", "two_after", "three_after", "four_after", "five_after"), names_to = "when")
```

# How does boxplot differ by days before and after year-high days
```{r}
ggplot(five_box_plot, aes(x = when, y = value)) + geom_boxplot()
```

